%Include a project management plan with all major milestones, tasks, and personnel assigned.

    For our project, we were able to split up our project among the group members for an even workload, as seen in Table 1. As seen on the table, we wanted to make sure everything was completed in a timely manner.\par

    \begin{table}[H]
        \begin{center}
        \begin{tabular}{|c|c|c|c|c|} \hline 
        \textbf{Task Name}& \textbf{Start}& \textbf{End}& \textbf{Duration}& \textbf{Assigned} \\ \hline
            Concept Sketch& 10/30& 10/30& 00:02:00&  Grant/Huy\\ \hline   
            Components Design& 11/07& 11/21& 14:00:00&  All Members\\ \hline
            Assembly& 11/21& 11/28& 07:00:00&  Huy/Devin\\ \hline 
            Detailed Drawings&11/07& 11/21& 14:00:00&  Grant\\ \hline 
            Assembly Drawings&11/21& 11/28& 07:00:00&  Grant\\ \hline 
            Motion Analysis&12/05& 12/5& 00:05:00&  Huy\\ \hline 
            Report&11/07& 12/05& 14:00:00&  All Members\\ \hline 
            Video&12/05& 12/05& 00:05:00&  All Members\\\hline
        \end{tabular}
        \end{center}
        \caption{Project Schedule as of \today}
        \label{tab:table1}
    \end{table}

    Grant and Huy started off with doing concept designs of our drone. They developed detailed drawings of our drone and talked about how our group wanted to proceed with the modeling. Grant was in charge of designing the body of the hat, Huy designed the propellers used, Devin designed the dowel that connected the propeller to the hat and Faisal designed the parts cover. We were able to complete our component design by our estimated end date of 11/21.

    Next came the assembly and drawings, where Grant made drawings of each of the parts, as seen below. Huy and Devin worked together to create the final assembly which took about 2 hours. Finally, Huy pieced together the motion analysis of our video while Devin worked to start our report. The final product of our drone was finished well in advanced and gave us an accurate representation of our original concept sketches.